---
title: "Spaghetti tube - Partner Payoffs (aka Phase 7)"
author: "Christoph Voelter"
date: "August 02, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (car)
library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(ggplot2)
library(scales)
library(gridExtra)
library(psych)
library(summarytools)
source("../../R scripts/Roger/diagnostic_fcns.r")
source("../../R scripts/Roger/glmm_stability.r")
source("../../R scripts/Roger/boxplotteR.r")
source("../../R scripts/Roger/boot_glmm.r")
source("../../R scripts/Roger/corr_exact.r")
load(file ="exp2_glmm1_CI.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE, warning = FALSE}
#Preparing code for mixed modeling. 
all.data <- read.table(file="data/Spaghetti_Tube_Phase7_data_for_r.txt", header=T, sep="\t")
str(all.data)
describeBy(all.data)


all.data<-all.data %>%
  mutate(BeggingGestures = na_if(BeggingGestures, "?")) %>%
  mutate(AttgetObeg = na_if(AttgetObeg, "?")) %>%
  mutate(Gesture = ifelse(BeggingGestures=="yes","yes",(ifelse(AttgetObeg=="yes","yes","no"))))

  
all.data<-droplevels(all.data)
all.data$Gesture=as.factor(all.data$Gesture)
view(dfSummary(all.data))

```





##Summary
Both the paired-samples t-test and a mixed model show a significant effect for condition. There was no significant interaction between session and condition. 


##Plotting data
```{r error=FALSE, echo=FALSE}

plot_individual <- all.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(NonsocialRoom4,SpaghettiTube, dir_dyad ) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>% 
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)

spaghetti.labs <- c("Tube: High", "Tube: Nothing")
names(spaghetti.labs) <- c("High", "Nothing")

p1<-ggplot(
  data=plot_individual, aes(NonsocialRoom4, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=interaction(NonsocialRoom4,SpaghettiTube)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Non-social apparatus",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
  facet_wrap(~ SpaghettiTube,labeller=labeller(SpaghettiTube=spaghetti.labs))



###Tool recipient data
rec.data <- read.table(file="data/Spaghetti_Tube_Phase7_data_for_r.txt", header=T, sep="\t")
rec.data$Highpass<-as.factor(rec.data$Highpass)
rec.data=subset(rec.data, tool_trans==1)
rec.data$tool_intube=droplevels(rec.data$tool_intube)
rec.data$tool_intube=as.integer(rec.data$tool_intube)-1
plot_individual_rec <- rec.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(NonsocialRoom4,SpaghettiTube,dir_dyad ) %>% 
  summarize(tool_in_Tube = mean(tool_intube))  %>% 
  add_count(tool_in_Tube)


p2<-ggplot(
  data=plot_individual_rec, aes(NonsocialRoom4, tool_in_Tube, group=dir_dyad)) +   
  geom_boxplot(aes(group=interaction(NonsocialRoom4,SpaghettiTube)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual_rec$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  #ylim(0,12)+
  labs(x="Non-social apparatus",y="Tool in Tube")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
  facet_wrap(~ SpaghettiTube,labeller=labeller(SpaghettiTube=spaghetti.labs))

#tiff("SpaghettiTube_room4 payoffs.tiff", width= 180, height= 120, units = "mm", res=150)
grid.arrange(p1, p2, nrow = 1, heights=unit(100, "mm"))
#dev.off()


```





```{r error=FALSE, echo=FALSE}
#Tool recipient: spaghetti tube
plot_individual2 <- all.data %>%
 # filter(NonsocialRoom3=="Low")%>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(SpaghettiTube, dir_dyad) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>%
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)

median_S.R4<-plot_individual2  %>%
  group_by(SpaghettiTube) %>% 
  summarize(tool_transfer2 = median(tool_transfer))  

p2<-ggplot(
  data=plot_individual2, aes(SpaghettiTube, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=SpaghettiTube), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual2$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,0.8)+
  labs(x="Tool recipient: social payoff",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))#+
  #ggtitle("Tool recipient: Social Payoff")

#Payoff tool giver
plot_individual3 <- all.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(NonsocialRoom3, dir_dyad) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>%
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)

median_NS.R3 <- plot_individual3  %>%
  group_by(NonsocialRoom3) %>% 
  summarize(tool_transfer2 = median(tool_transfer))  

p1 <- ggplot(
  data=plot_individual3, aes(NonsocialRoom3, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=NonsocialRoom3), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual3$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4)+
  ylim(0,0.8)+
  labs(x="Tool giver: Non-social payoff",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))#+      ggtitle("Tool giver: Non-social Payoff")

#Presence
plot_individual4 <- all.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(Presence, dir_dyad) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>% 
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)

median_Presence <- plot_individual4  %>%
  group_by(Presence) %>% 
  summarize(tool_transfer2 = median(tool_transfer))  

p3 <- ggplot(
  data=plot_individual4, aes(Presence, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=Presence), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual4$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,0.8)+
  labs(x="Presence of tool recipient",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))#+
 # ggtitle("Presence of tool recipient" )

#tiff("SpaghettiTube_tool_transfer_predictors.tiff", width= 180, height= 120, units = "mm", res=150)
grid.arrange(p1, p2,p3, nrow = 1, heights=unit(100, "mm"))
#dev.off()


```

###Plotting effect of gestures on tool transfer

```{r error=FALSE, echo=FALSE}

plot_individual5 <- model.data.chimp %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(Gesture, dir_dyad) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>% 
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)
  
  
plot_individual5$diff_score=plot_individual5$tool_transfer[plot_individual5$Gesture=="yes"]-plot_individual5$tool_transfer[plot_individual5$Gesture=="no"]
plot_individual5 <- plot_individual5 %>%
  add_count(diff_score, name = "n_diff")


median_gesture_chimp<-plot_individual5  %>%
  group_by(Gesture) %>% 
  summarize(tool_transfer2 = median(tool_transfer))  

p4<-ggplot(
  data=plot_individual5, aes(Gesture, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=Gesture), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual5$n, colour = "darkgrey", alpha=0.6) +
  geom_line(lty=2, alpha=0.8, colour="darkgrey")+
  ylim(0,0.8)+
  labs(x="Recipient gestures",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
  ggtitle("Chimpanzee")

#ggsave("SpaghettiTube_tooltransfer.tiff", width = 10, height = 10, units = "cm")

p4


plot_individual6 <- model.data.orang %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(Gesture, dir_dyad) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>% 
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)

median_gesture_orang<-plot_individual6  %>%
  group_by(Gesture) %>% 
  summarize(tool_transfer2 = median(tool_transfer))  

p5<-ggplot(
  data=plot_individual6, aes(Gesture, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=Gesture), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual6$n, colour = "darkgrey", alpha=0.6) +
  geom_line(lty=2, alpha=0.8, colour="darkgrey")+
  ylim(0,0.8)+
  labs(x="Recipient gestures",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), axis.title.y = element_blank(), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
  ggtitle("Orangutan")

#ggsave("SpaghettiTube_tooltransfer.tiff", width = 10, height = 10, units = "cm")

p5

#tiff("SpaghettiTube_tool_transfer_gestures.tiff", width= 120, height= 120, units = "mm", res=150)
grid.arrange(p4, p5, nrow = 1, heights=unit(100, "mm"))
#dev.off()






```






\pagebreak  
``

## GLMM

#GLMM without gesture
``` {r mixed modeling, error=TRUE}

# centering variables for modeling

model.all.data <- all.data %>% 
  mutate(z.Trial = scale(Trial, scale = T, center = T),
         z.Session = scale(Session, scale=T, center=T),
         NonsocialRoom3.c = scale(as.numeric(NonsocialRoom3), scale=F,center=T),
         SpaghettiTube.c = scale(as.numeric(SpaghettiTube), scale=F,center=T),
         NonsocialRoom4.c = scale(as.numeric(NonsocialRoom4), scale=F,center=T),
         Presence.c = scale(as.numeric(Presence), scale=F,center=T),
         Species.c = scale(as.numeric(Species), scale=F,center=T))


mm.S1 <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube+NonsocialRoom4  + Presence+
             Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence|Room3)+ 
             (0+Presence|Room4)+
             (0+Presence|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)
             , data = model.all.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```

####Model output
  + Coefficients
```{r}
round(summary(mm.S1)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop.mm.S1=drop1(mm.S1, test="Chisq")
round(xdrop.mm.S1,3)
```


#GLMM with gesture

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="tool_trans ~ NonsocialRoom3 + SpaghettiTube*NonsocialRoom4+ Species+ Session+Trial+Presence+Gesture ",
                   re="(1|Room3)+ (1|Room4)+ (1|Dyad)", data=all.data)
xx.fe.re$summary
```



``` {r mixed modeling, error=TRUE}

# centering variables for modeling

model.data <- all.data %>% 
  na.omit(cols=Gesture)%>% 
  mutate(z.Trial = scale(Trial, scale = T, center = T),
         z.Session = scale(Session, scale=T, center=T),
         BeggingGestures = relevel(BeggingGestures, ref = "yes"),
         AttgetObeg = relevel(AttgetObeg, ref = "yes"),
         NonsocialRoom3.c = scale(as.numeric(NonsocialRoom3), scale=F,center=T),
         SpaghettiTube.c = scale(as.numeric(SpaghettiTube), scale=F,center=T),
         NonsocialRoom4.c = scale(as.numeric(NonsocialRoom4), scale=F,center=T),
         Gesture.c = as.numeric(Gesture)-mean(as.numeric(Gesture)),
         Presence.c = scale(as.numeric(Presence), scale=F,center=T),
         Species.c = scale(as.numeric(Species), scale=F,center=T))

```

#Exp2, GLMM 1 with Gesture and Gesture*Species interaction and without the interaction


``` {r mixed modeling, error=TRUE}


## code to run the model
mm01 <- glmer(tool_trans~NonsocialRoom3 + (SpaghettiTube*NonsocialRoom4)  + Presence+ Gesture*Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)+
             
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room3)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room4)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Dyad) 
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```



####Null model	 
```{r}	 
mm01.null <- glmer(tool_trans~z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
               
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)+
             
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room3)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room4)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Dyad) 
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```


####Full-null model comparison
```{r}	 
anova(mm01, mm01.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm01)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop.mm1=drop1(mm01, test="Chisq")
round(xdrop.mm1,3)
```





``` {r mixed modeling, error=TRUE}

## code to run the model
mm01.2 <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube + NonsocialRoom4  + Presence+ Gesture* Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```
####Model output
  + Coefficients
```{r}
round(summary(mm01.2 )$coefficients, 3)
```
 
mean and SE of the covariates: 
```{r}
mean(model.data$Session)
sd(model.data$Session)

mean(model.data$Trial)
sd(model.data$Trial)

``` 




  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop.mm01.2 =drop1(mm01.2 , test="Chisq")
round(xdrop.mm01.2,6)
```


#Exp 2, GLMM 1 with Gesture and Gesture*Species interaction: Species relevelled




``` {r mixed modeling, error=TRUE}
model.data$Species2<-relevel(model.data$Species, "Orangutan")

## code to run the model
mm01.2_Species <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube +NonsocialRoom4  + Presence+ Gesture*Species2+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```


####Model output
  + Coefficients
```{r}
round(summary(mm5_Species2)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop5_Species2=drop1(mm5_Species2, test="Chisq")
round(xdrop5_Species2,3)
```
```{r}
save.image("exp2_glmm1_CI.RData")
```

```{r}
pred.mm01.2.gesture <- glmer(tool_trans~NonsocialRoom3.c + SpaghettiTube.c + NonsocialRoom4.c  + Presence.c+ Gesture* Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)



```

```{r}
pred.mm01.2.NS3 <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube.c + NonsocialRoom4.c  + Presence.c+ Gesture.c* Species.c+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)



```

```{r}
pred.mm01.2.Room4 <- glmer(tool_trans~NonsocialRoom3.c + SpaghettiTube + NonsocialRoom4  + Presence.c+ Gesture.c* Species.c+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)



```


```{r}
pred.mm01.2.ST4 <- glmer(tool_trans~NonsocialRoom3.c + SpaghettiTube + NonsocialRoom4.c  + Presence.c+ Gesture.c* Species.c+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)



```

```{r}
pred.mm01.2.Presence <- glmer(tool_trans~NonsocialRoom3.c + SpaghettiTube.c + NonsocialRoom4.c  + Presence+ Gesture.c* Species.c+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)



```

```{r}
save.image("exp2_glmm1_CI.RData")
```
