---
title: "Spaghetti tube - Partner Payoffs  (aka Phase 7) - Tool recipient performance"
author: "Christoph Voelter"
date: "August 07, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (car)
library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(ggplot2)
library(scales)
library(gridExtra)
library(psych)
library(summarytools)
source("../../R scripts/Roger/diagnostic_fcns.r")
source("../../R scripts/Roger/glmm_stability.r")
source("../../R scripts/Roger/boxplotteR.r")
source("../../R scripts/Roger/boot_glmm.r")
source("../../R scripts/Roger/corr_exact.r")
#load(file ="GLMM_SpaghettiTube_partnerPayoffs_toolrecipient.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE, warning = FALSE}
#Preparing code for mixed modeling. 
all.data <- read.table(file="data/Spaghetti_Tube_Phase7_data_for_r.txt", header=T, sep="\t")
all.data$Highpass<-as.factor(all.data$Highpass)
all.data=subset(all.data, tool_trans==1)
all.data$tool_intube=droplevels(all.data$tool_intube)
all.data$tool_intube=as.integer(all.data$tool_intube)-1
str(all.data)
describeBy(all.data)
view(dfSummary(all.data))

```





##Summary
Both the paired-samples t-test and a mixed model show a significant effect for condition. There was no significant interaction between session and condition. 


##Plotting data
```{r error=FALSE, echo=FALSE}

plot_individual <- all.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(NonsocialRoom4,SpaghettiTube,dir_dyad ) %>% 
  summarize(tool_in_Tube = mean(tool_intube))  %>% 
  add_count(tool_in_Tube)

ggplot(
  data=plot_individual, aes(interaction(NonsocialRoom4,SpaghettiTube), tool_in_Tube, group=dir_dyad)) +   
  geom_boxplot(aes(group=interaction(NonsocialRoom4,SpaghettiTube)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  #ylim(0,12)+
  labs(x="Condition",y="Tool in Tube")+
  theme_few()#+
  #scale_y_continuous(breaks=seq(0,12,2))


```
```{r error=FALSE, echo=FALSE}
#Tool recipient: spaghetti tube
plot_individual2 <- all.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(SpaghettiTube, dir_dyad) %>% 
  summarize(tool_in_tube = mean(tool_intube))  %>%
  mutate(tool_in_tube = round(tool_in_tube/0.01)*0.01)%>%
  add_count(tool_in_tube)

median_S.R4<-plot_individual2  %>%
  group_by(SpaghettiTube) %>% 
  summarize(tool_in_tube2 = median(tool_in_tube))  

p2<-ggplot(
  data=plot_individual2, aes(SpaghettiTube, tool_in_tube, group=dir_dyad)) +   
  geom_boxplot(aes(group=SpaghettiTube), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual2$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Tool recipient: social payoff",y="Tool in Tube")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))#+
  #ggtitle("Tool recipient: Social Payoff")

#Payoff tool recipient: NS option
plot_individual3 <- all.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(NonsocialRoom4, dir_dyad) %>% 
  summarize(tool_in_tube = mean(tool_intube))  %>%
  mutate(tool_in_tube = round(tool_in_tube/0.01)*0.01)%>%
  add_count(tool_in_tube)

median_NS.R4 <- plot_individual3  %>%
  group_by(NonsocialRoom4) %>% 
  summarize(tool_in_tube2 = median(tool_in_tube))  

p1 <- ggplot(
  data=plot_individual3, aes(NonsocialRoom4, tool_in_tube, group=dir_dyad)) +   
  geom_boxplot(aes(group=NonsocialRoom4), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual3$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4)+
  ylim(0,1)+
  labs(x="Tool recipient: Non-social payoff",y="Tool in Tube")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))#+      ggtitle("Tool recipient: Non-social Payoff")


#HighPass
plot_individual4 <- all.data %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(Highpass, dir_dyad) %>% 
  summarize(tool_in_tube = mean(tool_intube))  %>%
  mutate(tool_in_tube = round(tool_in_tube/0.01)*0.01)%>%
  add_count(tool_in_tube)

median_Presence <- plot_individual4  %>%
  group_by(Highpass) %>% 
  summarize(tool_in_tube2 = median(tool_in_tube))  

p3 <- ggplot(
  data=plot_individual4, aes(Highpass, tool_in_tube, group=dir_dyad)) +   
  geom_boxplot(aes(group=Highpass), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual4$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="High tool passing",y="Tool in Tube")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))#+
 # ggtitle("High tool passing" )

#tiff("SpaghettiTube_tool_transfer_predictors.tiff", width= 180, height= 120, units = "mm", res=150)
grid.arrange(p1, p2,p3, nrow = 1, heights=unit(100, "mm"))
#dev.off()

#ggsave("SpaghettiTube_tooltranser.tiff", width = 18, height = 10, units = "cm")


```

###Plotting effect of gestures on tool transfer

```{r error=FALSE, echo=FALSE}

plot_individual5 <- model.data.chimp %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(Gesture, dir_dyad) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>% 
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)
  
  
plot_individual5$diff_score=plot_individual5$tool_transfer[plot_individual5$Gesture=="yes"]-plot_individual5$tool_transfer[plot_individual5$Gesture=="no"]
plot_individual5 <- plot_individual5 %>%
  add_count(diff_score, name = "n_diff")


median_gesture_chimp<-plot_individual5  %>%
  group_by(Gesture) %>% 
  summarize(tool_transfer2 = median(tool_transfer))  

p4<-ggplot(
  data=plot_individual5, aes(Gesture, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=Gesture), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual5$n, colour = "darkgrey", alpha=0.6) +
  geom_line(lty=2, alpha=0.8, colour="darkgrey")+
  ylim(0,0.8)+
  labs(x="Gesture",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
  ggtitle("Chimpanzee")

ggsave("SpaghettiTube_tooltransfer.tiff", width = 10, height = 10, units = "cm")

p4


plot_individual6 <- model.data.orang %>%
  mutate(dir_dyad = paste(Room3, Room4, sep = '_'))%>%
  group_by(Gesture, dir_dyad) %>% 
  summarize(tool_transfer = mean(tool_trans))  %>% 
  mutate(tool_transfer = round(tool_transfer/0.01)*0.01)%>%
  add_count(tool_transfer)

median_gesture_orang<-plot_individual6  %>%
  group_by(Gesture) %>% 
  summarize(tool_transfer2 = median(tool_transfer))  

p5<-ggplot(
  data=plot_individual6, aes(Gesture, tool_transfer, group=dir_dyad)) +   
  geom_boxplot(aes(group=Gesture), width=0.9, outlier.colour="white")+
  geom_point(size = plot_individual6$n, colour = "darkgrey", alpha=0.6) +
  geom_line(lty=2, alpha=0.8, colour="darkgrey")+
  ylim(0,0.8)+
  labs(x="Gesture",y="Tool transfer")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
  ggtitle("Orangutan")

#ggsave("SpaghettiTube_tooltransfer.tiff", width = 10, height = 10, units = "cm")

p5

tiff("SpaghettiTube_tool_transfer_gestures.tiff", width= 120, height= 120, units = "mm", res=150)
grid.arrange(p4, p5, nrow = 1, heights=unit(100, "mm"))
dev.off()






```

```{r error=FALSE, echo=FALSE}

theme_set(theme_classic())

# Plot
ggplot(all.data, aes(x=factor(chimp), y=factor(trial_total), group=pull_action)) + 
  geom_point(stat='identity', aes(shape=pull_action, col=correct), size=5) +
  scale_shape_manual(values=c(7,15), name="Ropes pulled")+
      scale_color_manual(name="Reward obtained", 
                     labels = c("no", "yes"), 
                     values = c("yes"="#00ba38", "no"="darkblue")) +
# 
#   geom_segment(aes(x=chimp, 
#                    xend=chimp, 
#                    y=min(trial), 
#                    yend=max(trial)), 
#              #  linetype="dashed", 
#                size=0.5,
#                colour="grey") +
#     geom_segment(aes(x=chimp, 
#                    xend=chimp, 
#                    y=min(7), 
#                    yend=max(18)), 
#              #  linetype="dashed", 
#                size=0.5,
#                colour="grey") +
#      geom_segment(aes(x=chimp, 
#                    xend=chimp, 
#                    y=min(19), 
#                    yend=max(24)), 
#               # linetype="dashed", 
#                size=0.5,
#                colour="grey") + 
 theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  axis.ticks = element_blank())+
  geom_hline(yintercept=6.5, linetype="dashed", "black", size=0.75)+
  geom_hline(yintercept=18.5, linetype="dashed", "black", size=0.75)+
 # scale_x_discrete(name ="Chimp ID")+
  scale_y_discrete(breaks=c(3,12,22),labels=c("Transparent 1", "Opaque", "Transparent 2"))+ #name= "Condition",
  guides(color = guide_legend(order = 2),
         shape = guide_legend(order = 1))+
  coord_flip()


```





\pagebreak  
``

## GLMM

###GLMM 01 with Room 4 interaction

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="tool_trans ~ NonsocialRoom3 + SpaghettiTube*NonsocialRoom4+ Species+ Session+Trial+Presence ",
                   re="(1|Room3)+ (1|Room4)+ (1|Dyad)", data=all.data)
xx.fe.re$summary
```

``` {r mixed modeling, error=TRUE}

# centering variables for modeling
model.recipient.data <- all.data %>% 
  filter(tool_trans==1)
  mutate(z.Trial = scale(Trial, scale = T, center = T),
         z.Session = scale(Session, scale=T, center=T),
         SpaghettiTube.c = scale(as.numeric(SpaghettiTube), scale=F,center=T),
         NonsocialRoom4.c = scale(as.numeric(NonsocialRoom4), scale=F,center=T),
         Highpass.c = scale(as.numeric(Highpass), scale=F,center=T))

## code to run the model
mm1 <- glmer(tool_intube~ SpaghettiTube*NonsocialRoom4  + Highpass +
             Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
               
             (0+Highpass.c|Room3)+ 
             (0+Highpass.c|Room4)+
             (0+Highpass.c|Dyad)+

             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)+
             
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room3)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room4)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Dyad) 
             , data = model.recipient.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```

```{r include=FALSE}
## save model output

save.image("mm1_SpaghettiTube_partnerPayoffs.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res, "multpos_model.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model.rds"), 3)
```

####Null model	 
```{r}	 
mm.1.null <- glmer(tool_trans~1+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+Presence|Room3)+ 
             (0+Presence|Room4)+
             (0+Presence|Dyad)+  
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)+
             
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room3)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room4)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Dyad) 
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm1, mm.1.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm1)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm1, test="Chisq")
round(xdrop1,3)
```

```{r}
tab_model(mm1, show.est = TRUE, show.se = TRUE, show.stat = TRUE, )#,file="test.doc", )

```


###GLMM02 without the interaction


``` {r mixed modeling2, error=TRUE}
mm2 <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube+NonsocialRoom4  + Presence+
             Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence|Room3)+ 
             (0+Presence|Room4)+
             (0+Presence|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```
####Null model	 
```{r}	 
mm.2.null <- glmer(tool_trans~1+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+Presence|Room3)+ 
             (0+Presence|Room4)+
             (0+Presence|Dyad)+  
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)
             
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```

####Full-null model comparison
```{r}	 
anova(mm2, mm.2.null, test="Chisq")
```


####Model output
  + Coefficients
```{r}
round(summary(mm2)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop2=drop1(mm2, test="Chisq")
round(xdrop2,3)
```




``` {r include=FALSE}
## save model output
#saveRDS(mm.2, "multpos_model.rds")
save.image("SpaghettiTube_partnerPayoffs_GLMMs_tool transfer.RData")
```

####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
boot.res2=boot.glmm(model.res=mm.2, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res2, "multpos_model2.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model2.rds"), 3)
```



#### check for colinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.mm1 <- glm(tool_trans ~ NonsocialRoom3 + SpaghettiTube+NonsocialRoom4  + Presence+
             Species+ z.Session+z.Trial
             , data = model.data
             
)
vif(col.mm1)
#no problem
```
-> no collinearity

####Model output
`````` {r plot mixed modeling, error=TRUE, warning=FALSE}

plot_model(mm2, type='est') 
plot_model(mm2, type='re') 
```


#GLMM with gesture

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="tool_trans ~ NonsocialRoom3 + SpaghettiTube*NonsocialRoom4+ Species+ Session+Trial+Presence+Gesture ",
                   re="(1|Room3)+ (1|Room4)+ (1|Dyad)", data=all.data)
xx.fe.re$summary
```



``` {r mixed modeling, error=TRUE}

# centering variables for modeling

model.data <- all.data %>% 
  na.omit(cols=Gesture)%>% 
  mutate(z.Trial = scale(Trial, scale = T, center = T),
         z.Session = scale(Session, scale=T, center=T),
         BeggingGestures = relevel(BeggingGestures, ref = "yes"),
         AttgetObeg = relevel(AttgetObeg, ref = "yes"),
         NonsocialRoom3.c = scale(as.numeric(NonsocialRoom3), scale=F,center=T),
         SpaghettiTube.c = scale(as.numeric(SpaghettiTube), scale=F,center=T),
         NonsocialRoom4.c = scale(as.numeric(NonsocialRoom4), scale=F,center=T),
         Gesture.c = as.numeric(Gesture)-mean(as.numeric(Gesture)),
         Presence.c = scale(as.numeric(Presence), scale=F,center=T))


## code to run the model
mm3 <- glmer(tool_trans~NonsocialRoom3 + (SpaghettiTube*NonsocialRoom4)  + Presence+ Gesture+
             Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)+
             
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room3)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room4)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Dyad) 
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```

####Null model	 
```{r}	 
mm.3.null <- glmer(tool_trans~1+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
               
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)+
             
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room3)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room4)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Dyad) 
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm3, mm.3.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm3)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop3=drop1(mm3, test="Chisq")
round(xdrop3,3)
```


#GLMM 4 with Gesture and without the interaction

``` {r mixed modeling, error=TRUE}


## code to run the model
mm4 <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube + NonsocialRoom4  + Presence+ Gesture+
             Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```

####Null model	 
```{r}	 
mm.4.null <- glmer(tool_trans~1+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
               
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm4, mm.4.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm4)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop4=drop1(mm4, test="Chisq")
round(xdrop4,3)
```

#### check for colinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.mm3 <- glm(tool_trans ~ NonsocialRoom3 + SpaghettiTube+NonsocialRoom4  + Presence+Gesture+
             Species+ z.Session+z.Trial
             , data = model.data
             
)
vif(col.mm3)
#no problem
```

#GLMM 5 with Gesture and Gesture*Species interaction and without the interaction




``` {r mixed modeling, error=TRUE}


## code to run the model
mm5int <- glmer(tool_trans~NonsocialRoom3 + (SpaghettiTube*NonsocialRoom4)  + Presence+ Gesture*Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)+
             
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room3)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Room4)+
             (0+I(SpaghettiTube.c*NonsocialRoom4.c)|Dyad) 
             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```

####Full-null model comparison
```{r}	 
anova(mm5int, mm.3.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm5int)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop5int=drop1(mm5int, test="Chisq")
round(xdrop5int,3)
```





``` {r mixed modeling, error=TRUE}

## code to run the model
mm5 <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube + NonsocialRoom4  + Presence+ Gesture* Species+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```
####Model output
  + Coefficients
```{r}
round(summary(mm5)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop5=drop1(mm5, test="Chisq")
round(xdrop5,3)
```

``` {r mixed modeling, error=TRUE}

model.data.orang<-model.data %>%
  filter(Species=="Orangutan")
str(model.data.orang)

## code to run the model
mm5.orang <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube + NonsocialRoom4  + Presence+ Gesture+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data.orang
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```


####Model output
  + Coefficients
```{r}
round(summary(mm5.orang)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop5.orang=drop1(mm5.orang, test="Chisq")
round(xdrop5.orang,3)
```


``` {r mixed modeling, error=TRUE}

model.data.chimp<-model.data %>%
  filter(Species=="Chimpanzee")
#str(model.data.chimp)

## code to run the model
mm5.chimp <- glmer(tool_trans~NonsocialRoom3 + SpaghettiTube + NonsocialRoom4  + Presence+ Gesture+ z.Session+z.Trial+
             (1|Room3)+(1|Room4)+ (1|Dyad)+
             
             (0+z.Session|Room3)+ 
             (0+z.Session|Room4)+
             (0+z.Session|Dyad)+
  
             (0+z.Trial|Room3)+ 
             (0+z.Trial|Room4)+
             (0+z.Trial|Dyad)+
             
             (0+NonsocialRoom3.c|Room3)+ 
             (0+NonsocialRoom3.c|Room4)+
             (0+NonsocialRoom3.c|Dyad)+
               
             (0+Presence.c|Room3)+ 
             (0+Presence.c|Room4)+
             (0+Presence.c|Dyad)+
              
             (0+Gesture.c|Room3)+ 
             (0+Gesture.c|Room4)+
             (0+Gesture.c|Dyad)+
             
             (0+SpaghettiTube.c|Room3)+ 
             (0+SpaghettiTube.c|Room4)+
             (0+SpaghettiTube.c|Dyad)+
             
             (0+NonsocialRoom4.c|Room3)+ 
             (0+NonsocialRoom4.c|Room4)+
             (0+NonsocialRoom4.c|Dyad)

             , data = model.data.chimp
             , family = binomial
             , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```


####Model output
  + Coefficients
```{r}
round(summary(mm5.chimp)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop5.chimp=drop1(mm5.chimp, test="Chisq")
round(xdrop5.chimp,3)
```
